Meta-analysis Manuscript Wrangling

### 2021-07-02 shared analysis files /manuscript_datavis_22jun21.Rmd
model selection and meta-analysis plots

## Acclimation without modifiers
```{r, echo=FALSE, message=FALSE}
simple_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_acclimation_model
```

## Acclimation with modifiers
```{r, echo=FALSE, message=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

# Acclimation data split out by CT data and other thermal performance metrics 
```{r, echo=FALSE, message=FALSE}
CT_acclim_data <- dat_acclim_ES %>%
  filter(resp_def %in% c("CTmax", "CT max", "CTmin", "LTmax", "LTmin", "Topt", "Tpref", "Thermal preference", "ULT50", "Scope of thermal tolerance (CTmax - CTmin)"))

## CT aggregated model 
```{r, echo=FALSE, message=FALSE}
CT_model <-rma.mv(yi, vi, data=CT_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
CT_model
```
## Remaining acclimation metrics model 
```{r, echo=FALSE, message=FALSE}
curve_model <- rma.mv(yi, vi, data=curve_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
curve_model
```

@@

## Non-linear averaging model with no modifiers
```{r, echo= FALSE, message=FALSE}
simple_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_full_var_model
```

## Non-linear averaging model with modifiers
```{r, echo = FALSE, message=FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

@@

>>>>

## Acclimation with temperature modifiers
```{r, echo=FALSE, message=FALSE}
temp_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, mods=~flux_range * mean_temp_reared,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
temp_acclimation_model
```

## Acclimation with trait modifiers
```{r, echo=FALSE, message=FALSE}
trait_acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
                                mods = ~exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
trait_acclimation_model
```

## Acclimation with all modifiers
```{r, echo=FALSE, message=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

@@

## Non-linear averaging model with temperature modifiers
```{r, echo= FALSE, message=FALSE}
temp_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
                                mods = ~flux_range * mean_temp_constant,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
temp_full_var_model
```

## Non-linear averaging model with trait modifiers
```{r, echo = FALSE, message=FALSE}
trait_full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
trait_full_var_model
```

## Non-linear averaging model with all modifiers
```{r, echo = FALSE, message=FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

```{r}
#Model selection

AIC(temp_acclimation_model, trait_acclimation_model, acclimation_model, temp_full_var_model, trait_full_var_model, full_var_model)
```

```{r}
normalized_acclim <- dat_acclim_ES %>% filter(between(yi, -5, 5))
normalized_var <- dat_full_var_ES  %>% filter(between(yi, -5, 5))

dummy_acclim <- rma.mv(yi, vi, data=normalized_acclim, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
dummy_var <- rma.mv(yi, vi, data=normalized_var, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
```

```{r}
install.packages("devtools")
install.packages("tidyverse")
install.packages("metafor")
install.packages("patchwork")
install.packages("R.rsp")

devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", method= 'libcurl', force = TRUE, build_vignettes = TRUE)
library(orchaRd)
library(patchwork)
I2_acclim <- i2_ml(dummy_var)
I2_var <-i2_ml(dummy_acclim)

p1 <- orchard_plot(dummy_acclim, mod = "Int", xlab = "Standardised mean difference", transfm = "none", )+
  annotate(geom = "text", x = 0, y = 1.5, label = "Acclimation")+
  annotate(geom = "text", x = -4.7, y = 1.5, label = paste0("italic(I)^{2} == ",
round(I2_acclim[1] * 100, 2)), color = "black", parse = TRUE, size = 5) + annotate(geom = "text",
x = -3.7, y = 1.49, label = "%", color = "black", parse = FALSE, size = 5)

p2 <- orchard_plot(dummy_var, mod = "Int", xlab = "Standardised mean difference", transfm = "none")+
  annotate(geom = "text", x = 0, y = 1.5, label = "Non-linear averaging and acclimation")+
  annotate(geom = "text", x = -4.1, y = 1.5, label = paste0("italic(I)^{2} == ",
round(I2_var[1] * 100, 2)), color = "black", parse = TRUE, size = 5) + annotate(geom = "text",
x = -3.1, y = 1.49, label = "%", color = "black", parse = FALSE, size = 5)
p1 / p2

```

```{r}
normalized_acclim %>%
  ggplot(aes(y=yi, x=as.factor(mean_temp_reared)))+
  geom_boxplot()+
  geom_point()

normalized_acclim %>%
  group_by(flux_range, mean_temp_reared) %>%
  summarise(yi=mean(yi)) %>%
  ggplot(aes(x=flux_range, y=yi, color=mean_temp_reared))+
  geom_point(size= 4)+
  geom_smooth(method="lm")
```

@@

# Supplementary code and models

## Acclimation data split out by CT data and other thermal performance metrics 
```{r, echo=FALSE, message=FALSE, results='hide'}
CT_acclim_data <- dat_acclim_ES %>%
  filter(resp_def %in% c("CTmax", "CT max", "CTmin", "LTmax", "LTmin", "Topt", "Tpref", "Thermal preference", "ULT50", "Scope of thermal tolerance (CTmax - CTmin)"))

## CT aggregated model 
```{r, echo=FALSE, message=FALSE, results='hide'}
CT_model <-rma.mv(yi, vi, data=CT_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
CT_model
```
## Remaining acclimation metrics model 
```{r, echo=FALSE, message=FALSE, results='hide'}
curve_model <- rma.mv(yi, vi, data=curve_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
curve_model
```
